One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-12-07 draft_05.tex
more or less done with breathing mode section

\affiliation{
  $^1$ Fudan University, Shanghai, China\\ 
  $^2$ Max Planck Institute for the Physics of Complex Systems, N{\"o}thnitzer Str.~38, 01187 Dresden, Germany\\
  $^3$ Department of Theoretical Physics, Maynooth University, Co. Kildare, Ireland
}

@@

%\begin{figure}[h]
%\centering
%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
%\caption{ground state Energy with $F_0$}
%\end{figure}
%\end{comment}

@@

At very small $F_0$, the energy is minimized by having the particles approximately equidistant, at
distance $\approx 2F_0/\omega_0^2$ from each other.  In this `solid'-like state, the low-lying
excitation involves independent oscillation of the particles around their equilibrium position.

In Fig.\ref{fig:GS1}, we can see this crossover from the ``solid-like" limit (left) to the
``hardcore gas" limit (right).  In between, there is a rich staircase-like structure, as the
particles attempt to minimize the interaction by being at distance $>1$ from as many other particles
as allowed by the trap energy.

@@

%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
\begin{figure}[h]
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre_Font18.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: Red for $F_0=2\times10^3$; Yellow for $F_0=3\times10^3$; Green for $F_0=1\times10^4$;  Blue for $F_0=1\times10^5$. Run with three different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}
%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%

@@

@@

%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
\begin{figure}[h]
\centering
\includegraphics[scale=0.2]{ZhiyuPictures/effective_potential.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}
%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%

>>>>

\affiliation{
  $^1$ Department of Physics and State Key Laboratory of Surface Physics, Fudan University, Shanghai 200433, China\\ 
  $^2$ Max Planck Institute for the Physics of Complex Systems, N{\"o}thnitzer Str.~38, 01187 Dresden, Germany\\
  $^3$ Department of Theoretical Physics, Maynooth University, Co. Kildare, Ireland
}

@@

@@

At very small $F_0$, the particles in the ground state are close enough to the trap center that each
particle interacts with every other particle.  Equating the interaction force due to all the other
particles with the trapping force, one finds that the position of the $i$-th particle is
\begin{equation}
x_i ~=~ \frac{2F_0}{m\omega_0^2} \left( i - \frac{N+1}{2} \right) ~=~ 2F_0 \left( i - \frac{N+1}{2} \right)
\end{equation}
where the particles are labeled $i=1$ to $i=N$ from left to right.  Thus the particles are
equidistant in this regime.  In this `solid'-like state, the low-lying
excitation involves independent oscillation of the particles around their equilibrium position.

In this regime, the distance between the leftmost and rightmost particles is at most $\sigma=1$.
Thus, this situation extends up to $F_0 = \frac{1}{2(N-1)}$.  For the $N=5$ case shown in Figure
\ref{fig:GS1}, this behavior is seen up to $F_0 < 1/8$.

In Figure \ref{fig:GS1}, we can see this crossover from the ``solid-like'' limit (left) to the
``hardcore gas'' limit (right).  In between, there is a rich staircase-like structure, as the
particles attempt to minimize the interaction by being at distance $>1$ from as many other particles
as is compatible with the trap energy.

@@

\subsection{Comparisons with numerical data}

%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
\begin{figure}[h]
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre_Font18.eps}
\caption{Dependence of breathing frequency, calculated for $N=20$ particles, on energy.  Different
  colors represent different $F_0$ --- red for $F_0=2\times10^3$, yellow for $F_0=3\times10^3$,
  green for $F_0=1\times10^4$, and blue for $F_0=1\times10^5$.  Runs with three different initial
  states are shown in each case.  In each run, the frequency is measured both in the time window
  0-100 (labeled as crosses) and in the time window 900-1000 (labeled as circles). The black dashed
  line is the prediction of Eq.~\eqref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}
%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%

@@

One might ask whether the breathing frequency predictions are also valid at late times, after the
system has `relaxed' from the initial line distribution in phase space to a more spread-out cloud,
as we have seen in Figure \ref{fig:Breathingfrequency2_1}.  In \ref{fig:Breathingfrequency4} we show
the breathing frequency calculated from $R(t)$ oscillations in the first 100 time units, and also
the frequency from data in a later time window. The frequencies appear to be overall stable and dependent
primarily on $F_0$ and $E$.

@@

%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% 
\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{ZhiyuPictures/effective_potential.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}
%%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%% FIGURE %%%%%
